---
title: "Horror movie ratings"
author: "Yifei Liu"
date: "10/22/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


load packages and dataset

```{r}

library(tidyverse)
library(tidytext)
library(glmnet)
library(scales)
library(broom)
library(Matrix)
detach("package:dplyr", unload = TRUE)
library(dplyr)
library(showtext)
font_add_google("Lato", regular.wt = 300, bold.wt = 700)
theme_set(theme_minimal())

horror_movies_raw <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-22/horror_movies.csv")

```

# David Robinson Analysis

```{r}
horror_movies <- horror_movies_raw %>%
  extract(title, "year", "\\((\\d\\d\\d\\d)\\)$", remove = F, convert = T) %>%
  mutate(budget = parse_number(budget)) %>%
  separate(plot, c("Director", "cast_sentence", "plot"), extra = "merge", sep = "\\. ", fill = "right") %>%
  distinct(title, .keep_all = T)


```


in this dataset, most movies are since 2012. 


```{r}
horror_movies %>%
  count(genres, sort = T)

horror_movies %>%
  count(language, sort = T)

horror_movies %>%
  count(budget, sort = T) # most budget numbers are missing 2/3

horror_movies %>%
  ggplot(aes(budget)) +
  geom_histogram() +
  scale_x_log10(labels = dollar_format())

```

Do higher budget movies end up in higher rated?



```{r}

horror_movies %>%
  ggplot(aes(budget, review_rating)) +
  geom_point() +
  scale_x_log10() +
  geom_smooth(method = "lm")


```
 
 
No relationship between budget and review ratings. how about move ratings and reviews

```{r}

horror_movies %>%
  mutate(movie_rating = fct_explicit_na(movie_rating, na_level = "(Missing)"),
         movie_rating = fct_lump(movie_rating, 5),
         movie_rating = fct_reorder(movie_rating, review_rating, na.rm = T)) %>%
  ggplot(aes(movie_rating, review_rating)) +
  geom_boxplot() +
  coord_flip()

# Need review: new function fct_explicit_na make sure na values appear in the find result 


horror_movies %>%
  filter(!is.na(movie_rating)) %>%
  mutate(movie_rating = fct_lump(movie_rating, 5)) %>%
  lm(review_rating ~ movie_rating, data = .) %>%
  anova()

```




```{r}
horror_movies %>%
  separate_rows(genres, sep = "\\| ") %>%
  mutate(genre = fct_lump(genres, 5)) %>%
  ggplot(aes(genre, review_rating)) +
  geom_boxplot()
```

some text analysis

```{r}
horror_movies_unnested <- horror_movies %>%
  unnest_tokens(word, plot) %>%
  anti_join(stop_words, by = "word") %>%
  filter(!is.na(word))

horror_movies_unnested %>%
  filter(!is.na(review_rating)) %>%
  group_by(word) %>%
  summarize(movies = n(),
            avg_rating = mean(review_rating)) %>%
  arrange(desc(movies)) %>%
  filter(movies >= 100) %>%
  mutate(word = fct_reorder(word, avg_rating)) %>%
  ggplot(aes(avg_rating, word)) +
  geom_point()


```



## Lasso regression for predicting review ratings based on words

```{r}
# check duplicated movie titles
horror_movies %>%
  count(title, sort = T)

movie_word_matrix <- horror_movies_unnested %>%
  filter(!is.na(review_rating)) %>%
  add_count(word) %>%
  filter(n >= 20) %>%
  count(title, word) %>%
  cast_sparse(title, word, n)

dim(movie_word_matrix) # total 2945 movie titles, and 459 words

rating <- horror_movies$review_rating[match(rownames(movie_word_matrix), horror_movies$title)]
lasso_model <- cv.glmnet(movie_word_matrix, rating)

```


```{r}

lasso_model$glmnet.fit %>%
  tidy() %>%
  filter(term %in% c("friends", "evil", "college", "haunted", "mother", "quickly", "unexpected", "seek", "teacher")) %>%
  ggplot(aes(lambda, estimate, color = term)) +
  geom_line() +
  scale_x_log10() + 
  geom_vline(xintercept = lasso_model$lambda.min) +
  geom_hline(yintercept = 0, lty = 2) # we can see as lambda change, the coefficient values also change, so we need to pick a desirable penality lambda for our model, we can use plot(lasso_model) to pick 

```


```{r}

lasso_model$glmnet.fit %>%
  tidy() 

plot(lasso_model) # this show as our predictor increase, in this case between 131 and 355, log(lambda) is -4, we better off without a predictor

lasso_model$glmnet.fit %>%
  tidy() %>%
  filter(lambda == lasso_model$lambda.min,
         term != "(Intercept)") %>%
  mutate(term = fct_reorder(term, estimate)) %>%
  ggplot(aes(term, estimate)) +
  geom_col() +
  coord_flip()

```


Throwing everything into a linear model: director, cast, genre, rating, plot words. 


```{r}

features <- horror_movies %>%
  filter(!is.na(review_rating)) %>%
  select(title, genres, Director, cast, movie_rating, language, release_country) %>%
  mutate(director = str_remove(Director, "Directed by ")) %>%
  gather(type, value, - title) %>%
  filter(!is.na(value)) %>%
  separate_rows(value, sep = "\\| ?") %>%
  unite(feature, type, value, sep = ": ") %>%
  mutate(n = 1)

movie_feature_matrix <- horror_movies_unnested %>%
  filter(!is.na(review_rating)) %>%
  count(title, feature = paste0("word: ", word)) %>%
  bind_rows(features) %>%
  add_count(feature) %>%
  filter(n >= 10) %>%
  cast_sparse(title, feature)

dim(movie_feature_matrix)


rating <- horror_movies$review_rating[match(rownames(movie_feature_matrix), horror_movies$title)]

feature_lasso_model <- cv.glmnet(movie_feature_matrix, rating)

  
```



```{r}

plot(feature_lasso_model)

feature_lasso_model$glmnet.fit %>%
  tidy() %>%
  filter(lambda == feature_lasso_model$lambda.1se,
         term != "(Intercept)") %>%
  mutate(term = fct_reorder(term, estimate)) %>%
  ggplot(aes(term, estimate)) +
  geom_col() +
  coord_flip() +
  labs(x = "",
       y = "Coefficient for predicting horro movie rating",
       title = "What affects a horro movie rating?",
       subtitle = "Based on a lasso regression to predict IMDB ratings of ~3000 movies") +
  theme(text = element_text(family = "Lato"))

```

What movie should I watch

```{r}

horror_movies %>%
  filter(str_detect(genres, "Comedy"),
         !is.na(budget),
         !is.na(movie_rating),
         movie_rating != "PG") %>%
  arrange(desc(review_rating)) %>%
  select(title, review_rating, plot, movie_rating, Director, budget, language)

```

what type of horror movies you into you can filter in this way. 












