---
title: "Hotel Booking"
author: "Yifei Liu"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F,
                      message = F, cache = T,
                      dpi = 180)
```

```{r}
library(tidyverse)
library(tidymodels)
library(skimr)
library(lubridate)
library(GGally)
library(zoo)
theme_set(theme_minimal())

hotels <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-11/hotels.csv')
```


# [Julia Silge Analysis - Modeling hotel bookings in R using tidymodels and recipes](https://www.youtube.com/watch?v=dbXDkEEuvCU&t=361s)

## EDA

```{r}
hotels_stays <- hotels %>%
  filter(is_canceled == 0) %>%
  mutate(children = case_when(children + babies > 0 ~ "children",
                              TRUE ~ "none"),
         required_car_parking_spaces = case_when(required_car_parking_spaces > 0 ~ "parking",
                                                 TRUE ~ "none")) %>%
  select(-is_canceled, -reservation_status, -babies)

```

I wanna see on average how many reservation been canceled.

```{r}

hotels %>%
  filter(year(reservation_status_date) < 2017,
         ymd(reservation_status_date) > ymd("2015-07-01")) %>%
  group_by(reservation_status_date) %>%
  summarise(
    total_booked = sum(is_canceled == 1, na.rm = T),
    n = n()
  ) %>%
  mutate(cancel_rate = total_booked / n,
         weeks_3_avg = rollmedian(cancel_rate, k = 21, fill = NA)) %>%
  ggplot(aes(reservation_status_date, weeks_3_avg)) + 
  geom_line() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Hotel cancel rate",
       subtitle = "Date from July 2015 to Jan 2017",
       x = "", y = "3 weeks moving average median") 

```

Hotels cancel rate hang around 35%, higher than I expected. 



```{r}

skim(hotels_stays)

```

```{r}

hotels_stays %>%
  mutate(arrival_date_month = factor(arrival_date_month,
                                     levels = month.name)) %>%
  count(arrival_date_month, children, hotel) %>%
  group_by(children, hotel) %>%
  mutate(proportion = n / sum(n)) %>%
  ggplot(aes(arrival_date_month, proportion, fill = children)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  facet_wrap(~hotel, nrow = 2) +
  scale_fill_viridis_d()


```

```{r}
hotels_stays %>%
  count(children, required_car_parking_spaces, hotel) %>%
  group_by(children, hotel) %>%
  mutate(proportion = n / sum(n)) %>%
  ggplot(aes(required_car_parking_spaces, proportion, fill = children)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  facet_wrap(~hotel, nrow = 2) +
  scale_fill_viridis_d()


```

multi-panel plots

```{r}
hotels_stays %>%
  select(children, adr,
         required_car_parking_spaces, 
         total_of_special_requests) %>%
  ggpairs(mapping = aes(color = children))


```


## Modeling with recipes

```{r}

hotels_df <- hotels_stays %>%
  select(children, hotel, arrival_date_month, meal, adr, adults,
         required_car_parking_spaces, total_of_special_requests,
         stays_in_week_nights, stays_in_weekend_nights) %>%
  mutate_if(is.character, factor)

```


data preprocessign and data enginnering. Normalization the data set, balance the training base on outcome 

```{r}

set.seed(1234)

hotel_split <- initial_split(hotels_df)

hotel_train <- training(hotel_split)
hotel_test <- testing(hotel_split)


hotel_rec <- recipe(children ~ ., data = hotel_train) %>%
  step_downsample(children) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  step_zv(all_numeric()) %>%
  step_normalize(all_numeric()) %>%
  prep()

test_proc <- bake(hotel_rec, new_data = hotel_test)


juice(hotel_rec) # rebalance dataset
```


```{r}

knn_spec <- nearest_neighbor() %>%
  set_engine("kknn") %>% # k nearest neighbor are sensitivy to scale and center
  set_mode("classification") 

knn_fit <- knn_spec %>%
  fit(children ~.,
      data = juice(hotel_rec))

knn_fit


tree_spec <- decision_tree() %>%
  set_engine("rpart") %>%
  set_mode("classification")

tree_fit <- tree_spec %>%
  fit(children ~.,
      data = juice(hotel_rec))

tree_fit

```


## Evaluate models

```{r}
set.seed(1234)

validation_splits <- mc_cv(juice(hotel_rec), prop = 0.9, strata = children)

knn_res <- fit_resamples(
  children ~.,
  knn_spec,
  validation_splits,
  control = control_resamples(save_pred = T)
)

knn_res %>%
  collect_metrics()


tree_res <- fit_resamples(
  children ~.,
  tree_spec,
  validation_splits,
  control = control_resamples(save_pred = T)
)

tree_res %>%
  collect_metrics()


```


```{r}

knn_res %>%
  unnest(.predictions) %>%
  mutate(model = "knn") %>%
  bind_rows(tree_res %>%
              unnest(.predictions) %>%
              mutate(model = "rpart")) %>%
  group_by(model) %>%
  roc_curve(children, .pred_children) %>%
  autoplot()

knn_res %>%
  unnest(.predictions) %>%
  conf_mat(children, .pred_class) %>%
  autoplot(type = "heatmap")

```



```{r}

knn_fit %>%
  predict(new_data = test_proc, type = "prob") %>%
  mutate(truth = hotel_test$children) %>%
  roc_auc(truth, .pred_children)

```

Test result as good as training data result. 




















