---
title: "Analyzing African-American Achievements"
author: "Yifei Liu"
date: "6/10/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(plotly)
library(WikipediR)
theme_set(theme_minimal())

tuesdata <- tidytuesdayR::tt_load('2020-06-09')
```


```{r}

tuesdata$firsts %>% View()

tuesdata$science %>% View()

```


## African American Systemic racism in snapshot: 

African Americna experience Systemic racism general direction timeline, 

- before civil war 1856, *slavery*. 
- After civil war, *convict leasing* begining 1846 end July 1, 1928. 
- After than *Jim Crow* begainning at the end of Reconstruction in 1877 and the beginning of the civil rights movement in the 1950s. 
- After jim crow fade away, *massive incracation* start 1970.


## EDA

### See general trend

```{r}
firsts <- tuesdata$firsts %>%
   mutate(person = str_remove(person, "[\\[\\(].*"),
         person = str_trim(person))

 firsts %>%
  ggplot(aes(year)) +
  geom_histogram()
 
 firsts %>%
   count(category, year, sort = T) %>%
   ggplot(aes(year, n)) +
   geom_point() +
   facet_wrap(~ category)
 
 
 firsts %>%
   count(category, sort = T) %>%
   mutate(category = fct_reorder(category, n)) %>%
   ggplot(aes(n, category)) +
   geom_col()

```


\


```{r}
g <- firsts%>%
  ggplot(aes(year, category, color = category,
             text = glue::glue("{ year }: { accomplishment }\n{ person }"))) +
  geom_point() +
  labs(y = "") +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "none") +
  labs(y = "Category", x = "year")

ggplotly(g, tooltip = "text") %>%
  layout(title = list(text = paste0('Timeline of some notable African American achievements',
                                    '<br>',
                                    '<sup>',
                                    'Source; https://en.wikipedia.org/wiki/List_of_African-American_inventors_and_scientists',
                                    '</sup>')),
         hovermode = "x")

```



### Science

```{r}

science <- tuesdata$science

science %>%
  separate_rows(occupation_s, sep =  "; ") %>%
  mutate(occupation = str_to_title(occupation_s)) %>%
  count(occupation, sort = T)

science %>%
  filter(str_detect(occupation_s, regex("statis", ignore_case = T))) %>%
  pull(occupation_s)

science %>%
  filter(str_detect(occupation_s, "statistician")) 

```


```{r}
library(rvest)

science_html <- science %>%
  mutate(html = map(links, possibly(read_html, NULL, quiet = FALSE)))

```


```{r}

extract_infobox <- . %>%
  html_node(".vcard") %>%
  html_table(header = FALSE) %>%
  as_tibble()


infoboxes <- science_html %>%
  filter(!map_lgl(html, is.null)) %>%
  mutate(infobox = map(html, possibly(extract_infobox, NULL))) %>%
  select(link = links, infobox) %>%
  unnest(infobox) %>%
  filter(X1 != "" | X2 != "" | X1 != "Scientific career") %>%
  rename(key = X1, value = X2)

science_infoboxes <- infoboxes %>%
  group_by(key) %>%
  mutate(name = first(key)) %>%
  filter(n() >= 10) %>%
  group_by(link) %>%
  ungroup() %>%
  distinct(name, key, .keep_all = TRUE) %>%
  spread(key, value)

```


```{r}

science_infoboxes %>%
  pull(`Known for`)
```






